PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-18 qfenv_paper/qf_environment.tex
Chang Intro Edit
included numbers from moustakas+2013
and expanded further on internal/external

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation. Many of these proposed processes have received observational support. \cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies. Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}). \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime. While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.

>>>>

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). \cite{Moustakas:2013aa}, for instance, find that since $z \sim 1.0$ the $\sim 50\%$ decline in the number density of massive star-forming galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$) is complemented by the rise in number density of intermediate-mass quiescent galaxies ($\mathcal{M}_{*} \approx 10^{9.5} - 10^{10}\mathcal{M}_{\odot}$), by a factor of $ 2-3$, and massive quiescent galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$ ), by $\sim 20\%$. On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.

Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies. Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein). However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.

%Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}). \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime. While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.

%Some of these proposed internal processes have received observational support. \cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies.
